\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}

\geometry{margin=1in}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.75em}
\setlist{itemsep=0.25em}

\newcommand{\pkg}[1]{\textsf{#1}}
\newcommand{\cmd}[1]{\texttt{\textbackslash #1}}
\newcommand{\file}[1]{\texttt{#1}}

\title{\pkg{FoilX} User Manual}
\author{}
\date{May 2026}

\begin{document}
\maketitle

\pkg{FoilX} is a minimal FoilTeX-inspired LaTeX slide class. It is implemented
as \file{foilx.cls}, loads the standard \file{article} class, and adds a small
set of commands for writing landscape slide decks with large Computer Modern
fonts.

This document describes the public interface provided by the current class
file. It does not describe features that are not implemented by
\file{foilx.cls}.

\section{Overview}

FoilX is intended for simple lecture or seminar slide decks. The class sets up
letter-sized landscape pages, a large sans-serif default text face, ragged-right
paragraphs, slide-friendly list spacing, and a footer that can show the current
section and page number.

A typical deck uses the following structure:

\begin{itemize}
  \item \cmd{maketitle} creates the title page.
  \item \cmd{makesection} creates a numbered section page.
  \item \cmd{makefoil} creates each content foil.
  \item \cmd{makeappendix} switches to appendix numbering.
  \item \cmd{makereference} creates a bibliography page.
\end{itemize}

\section{Installation}

For a single talk, copy \file{foilx.cls} next to your main \file{.tex} file:

\begin{verbatim}
my-talk/
  talk.tex
  foilx.cls
\end{verbatim}

Then select the class in the usual way:

\begin{verbatim}
\documentclass{foilx}
\end{verbatim}

For regular use, install \file{foilx.cls} in a directory searched by your TeX
distribution, such as a local \file{texmf} tree. After installation, refresh
your TeX filename database if your distribution requires it.

\section{Quick Start}

The following complete deck uses the main FoilX commands:

\begin{verbatim}
\documentclass{foilx}

\title{A Short Talk}
\author{Ada Lovelace}
\date{\today}
\info{Example seminar}

\begin{document}
\maketitle

\makesection{Motivation}

\makefoil{A first foil}
\begin{itemize}
  \item FoilX uses large slide-friendly type.
  \item Each foil starts on a new landscape page.
  \item Footers show the current section and page number.
\end{itemize}

\makefoil{A second foil}
\[
  E = mc^2
\]

\makeappendix

\makefoil{Backup material}
Appendix foils are numbered A1, A2, and so on.
\end{document}
\end{verbatim}

Compile the deck with a standard LaTeX engine:

\begin{verbatim}
pdflatex talk.tex
\end{verbatim}

\section{Class Options}

FoilX currently defines one class option:

\begin{description}
  \item[\texttt{lecture}] Reset page numbering at each section and print foil
  numbers as \texttt{section--page}, for example \texttt{2--3}. Without this
  option, normal page numbering is used. Appendix foils use \texttt{A1},
  \texttt{A2}, and so on in both modes.
\end{description}

Use the option like this:

\begin{verbatim}
\documentclass[lecture]{foilx}
\end{verbatim}

If \file{hyperref} is loaded in lecture mode, FoilX sets
\texttt{hypertexnames=false} at the beginning of the document. This avoids
duplicate page anchors when page numbers reset for each section.

\section{Command Reference}

\begin{description}
  \item[\cmd{info}\texttt{\{text\}}] Store metadata shown in small type on
  section title pages. Typical values include a course name, seminar name, or
  event label.

  \item[\cmd{maketitle}] Create the title page using LaTeX's standard
  \cmd{title}, \cmd{author}, and \cmd{date} values. The title page is numbered
  internally as page \texttt{0}, so it does not print a normal footer.

  \item[\cmd{makesection}\texttt{\{title\}}] Start a new numbered section on a
  new page. The section title is remembered for later foil footers. In
  \texttt{lecture} mode, the page counter is reset to \texttt{1}.

  \item[\cmd{makefoil}\texttt{\{title\}}] Start a content foil on a new page
  with a centered title. The footer prints the current section title on the left
  and the page number on the right.

  \item[\cmd{makeappendix}] Start the appendix. FoilX inserts an appendix title
  page, clears the normal section footer, and numbers later appendix foils as
  \texttt{A1}, \texttt{A2}, and so on.

  \item[\cmd{makereference}\texttt{[size]\{bib-file\}}] Start a bibliography
  page using LaTeX's \cmd{bibliography} command and the \texttt{alpha}
  bibliography style. The optional \texttt{size} argument defaults to
  \cmd{small}; pass another declaration such as \cmd{footnotesize} if the
  reference list is long.

  \item[\cmd{vf}] Insert stretchable vertical space using
  \cmd{vspace*}\texttt{\{\cmd{fill}\}}. This is useful for pushing material
  toward the bottom of a foil.
\end{description}

\section{Layout And Typography}

FoilX configures the page as landscape letter paper, with an 11 inch width and
an 8.5 inch height. It sets the PDF page size to the same dimensions.

The default family is sans serif. Normal body text is set at a large
slide-oriented size, with larger display sizes available through the standard
\cmd{large}, \cmd{Large}, \cmd{LARGE}, \cmd{huge}, and \cmd{Huge} declarations.
Paragraphs are ragged right with no indentation, and lists use wider label
spacing suitable for projected slides.

The class loads \file{fix-cm}, \file{enumitem}, and \file{graphicx}. You may
load additional packages in your document preamble as usual.

\section{Appendix And References}

Call \cmd{makeappendix} once before backup slides:

\begin{verbatim}
\makeappendix

\makefoil{Additional Details}
This foil is numbered A1.
\end{verbatim}

For bibliographies, create a normal BibTeX file and call \cmd{makereference}:

\begin{verbatim}
\makereference{talk}
\end{verbatim}

This reads entries from \file{talk.bib}. The class selects the \texttt{alpha}
bibliography style.

\section{Complete Example Deck}

This example shows a small lecture-mode deck with title, sections, foils, and
appendix material.

\begin{verbatim}
\documentclass[lecture]{foilx}
\usepackage{amsmath}

\title{FoilX Demonstration}
\author{Ada Lovelace \\ Charles Babbage}
\date{\today}
\info{Analytical Engines 101}

\begin{document}
\maketitle

\makesection{A Simple Argument}

\makefoil{The Main Idea}
\begin{itemize}
  \item A section page introduces a topic.
  \item Foils after that section show the section title in the footer.
  \item In lecture mode, this foil is numbered 1--2.
\end{itemize}

\makefoil{A Formula}
\[
  \sum_{k=1}^{n} k = \frac{n(n+1)}{2}
\]

\makesection{Another Topic}

\makefoil{A Centered Ending}
Some slide text can appear near the top.

\vf

This line is pushed toward the bottom.

\makeappendix

\makefoil{Backup}
Appendix numbering is independent of lecture-mode section numbering.
\end{document}
\end{verbatim}

\section{License}

FoilX is distributed under the Apache License 2.0. See the repository
\file{LICENSE} file for the full license text.

\end{document}
